---
title: "Lab 02 - Take a sad plot and make it better"
author: "Group Members: Jack, Keyu, Aidan and Hrissy"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
staff <- read_csv("data/instructional-staff.csv")
view(staff)
```


--------


Team member 1 should pull to download updates and begins here.



### Exercise 1
55


Team member 1 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 2 should pull to download updates and begins here.

### Exercise 2

```{r staff-long-create}
staff_long <- staff %>%
  pivot_longer(
    cols = -faculty_type, 
    names_to = "year",
    values_to = "values"
    )
```


### Exercise 3

*Remove this text and add your answer here.*

```{r staff-long-inspect}
#Yes, correct
```


Team member 2 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 3 should pull to download updates and begins here.


### Exercise 4

*Remove this text and add your answer here.*

```{r lineplot-1}
staff_long %>%
  ggplot(aes(x = year, y = values, color = faculty_type)) +
  geom_line()

```

The issue is that there are no lines on the graph because there the data is not grouped

### Exercise 5

*Remove this text and add your answer here.*

```{r lineplot-2}
staff_long %>%
  ggplot(aes(x = year, y = values, color = faculty_type, group = faculty_type)) +
  geom_line()
```

Part-time faculty has increased greatly over time
Full-time tenured has decreased over time
Full-time tenure track has also decreased
Graduate Student and Full-time non tenure have remained relatively constant


Team member 3 should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 6

*Remove this text and add your answer here.*

```{r lineplot-3}
staff_long %>%
  ggplot(aes(x = year, y = values, color = faculty_type, group = faculty_type)) +
  geom_line() +
  labs(x = "Year", y = "Number of Faculty", title = "Faculty type trends from 1975 to 2011", color = "Faculty Type", caption = "American Association of University Professors (AAUP) data 
  showing trends in instructional staff employees between 
       1975 and 2011")
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 7

*Remove this text and add your answer here. No code needed for this exercise!*


### Exercise 8

*Remove this text and add your answer here.*

```{r lineplot-4}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

All team members should pull to download all updates.


